\MakeUppercase{Measuring polygonal niceness} \thanks{ This paper constitutes the completion of the final project for AMS 545 ``Computational Geometry''. }

### 2018-05-04 paper/main.tex
New abstract
Provisionally done with the paper

@@

\begin{abstract}
\end{abstract}

@@

We evaluate our measurements on randomly generated polygons with vertices in the
unit square $[0,1] \times [0,1]$. We consider collections of such polygons of
10, 50, and 100 vertices. In Figure \ref{fig:delta-alpha} and Figure
\ref{fig:delta-chordarc}, we measure the effect on
polygons of 10 vertices of sweeping $\delta$ between $0.05$ and $1$ on the
resulting measurements. Figure \ref{fig:alph-inft-10} shows a comparison of
$\alpha$-fatness and relative ${\chordarc}_{\infty}$ scores for polygons on 10
vertices.  Figure \ref{fig:alph-one-50} shows a comparison of $\alpha$-fatness
and relative ${\chordarc}_1$ scores for polygons on 50 vertices. Figure
\ref{fig:alph-inft-100} shows a comparison of $\alpha$-fatness and relative
${\chordarc}_{\infty}$ scores for polygons on 100 vertices.

@@

\begin{enumerate}
  \item Comment on the results.
  \item Talk about applications to Gerrymandering.
\end{enumerate}

\medskip

>>>>

\setcounter{tocdepth}{1} % -- part,chapters,sections

@@

\begin{abstract}
  The $\alpha$-fatness and chord-arc scores as measures of the ``niceness'' of
  polygons are developed and explored, with initial theoretical and empirical
  results. 
\end{abstract}

@@

We evaluate our measurements on randomly generated polygons with vertices in the
unit square $[0,1] \times [0,1]$. We consider collections of such polygons of
10, 50, and 100 vertices. In Figure \ref{fig:delta-alpha} and Figure
\ref{fig:delta-arc}, we measure the effect on
polygons of 10 vertices of sweeping $\delta$ between $0.05$ and $1$ on the
resulting measurements. Figure \ref{fig:alph-inft-10} shows a comparison of
$\alpha$-fatness and relative ${\chordarc}_{\infty}$ scores for polygons on 10
vertices.  Figure \ref{fig:alph-one-50} shows a comparison of $\alpha$-fatness
and relative ${\chordarc}_1$ scores for polygons on 50 vertices. Figure
\ref{fig:alph-inft-100} shows a comparison of $\alpha$-fatness and relative
${\chordarc}_{\infty}$ scores for polygons on 100 vertices.

@@
